Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-30 tests-wavepool.tex
Fixed typo in wavepool.  In answer to Sam, there are no red points outside the refined region (which is purely static, no AMR).  The figure quality is not ideal, so perhaps that is where the confusion comes from -- my eps backend on matplotlib doesnt render the grey properly, so I generated png and converted.

Figure~\ref{fig.wavepool} shows the evolution of the wave at three different times ($t = 0.2, 0.3$ and 0.8) for three of our solvers (PPM, Zeus, and MUSCL).  In all panels, the shaded regions denote the statically refined region. The leftmost column show the wave just before it enters the refined region so that we can gauge how the solver is operating in the absence of AMR.  The center column shows the wave after it has fully entered the refined region.  The rightmost column shows the wave well after it has exited the refined region.

With the PPM solver, we notice that even before the wave reaches the refined region it has been slightly damped. This is not unexpected for such a short wavelength mode, even for high-order solvers such as PPM.  The remaining panels demonstrate that the wave cleanly enters and exits the refined region.  No significant reflection is seen on either entry or exit, and the amount of damping is mild.

>>>>

Figure~\ref{fig.wavepool} shows the evolution of the wave at three different times ($t = 0.2, 0.3$ and 0.8) for three of our solvers (PPM, Zeus, and MUSCL).  In all panels, the shaded regions denote the statically refined region. The leftmost column shows the wave just before it enters the refined region so that we can gauge how the solver is operating in the absence of AMR.  The center column shows the wave after it has fully entered the refined region.  The rightmost column shows the wave well after it has exited the refined region.

With the PPM solver, we notice that even before the wave reaches the refined region it has been slightly damped. This is not unexpected for such a short wavelength mode, even for higher-order solvers such as PPM.  The remaining panels demonstrate that the wave cleanly enters and exits the refined region.  No significant reflection is seen on either entry or exit, and the amount of damping is mild.
